Ages of Stars and Planets Observed by Kepler

### 2024-04-22 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{gyromodeldispersion.pdf}
		}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{li_vs_teff_koi_X_S19S21dquality_eagles_showpoints_nodata.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf The models.}
    Points represent $10^4$ draws from model probability distributions
    that have been fitted to observed rotation periods
    \citep{Bouma_2023} and lithium equivalent widths
    \citep[EWs;][]{Jeffries_2023} of stars in open clusters.  Lines
    are the ``mean models'' at various ages; the asymmetric intrinsic
    dispersion in rotation and lithium about these mean models, which
    is what the models fit, sets the theoretical precision limit for
    both age-dating methods.		Additional sources of uncertainty,
    including measurement uncertainty, impose further limits on
    achievable age precision.  These models are calibrated using open
    clusters younger than 4\,Gyr.  The displayed points assume an
    unphysical uniform distribution in temperature for visual clarity.
    The sizes of the points are the same in each panel, so that low
    apparent density signifies greater dispersion around the mean.
		\label{fig:models}
	}
\end{figure*}

@@

@@

\startlongtable
\begin{deluxetable*}{lllllllrrrrrr}
	%\tabletypesize{\footnotesize}
	\tabletypesize{\scriptsize}
	\tablecaption{Young planets and planet candidates.
		%The non-truncated machine readable versions are accessible both
		%through the online journal, and at
		%\url{https://zenodo.org/record/8327508}.
		\label{tab:youngplanets}}
	%\toprule
	%\midrule
	%\endhead
	\startdata
  KOI & Kepler &  $T_{\rm eff}$ & $P_{\rm rot}$ & EW$_{\rm Li}$ & $t_{\rm gyro}$ & $t_{\rm Li} $ & $R_{\rm p}$ & $P_{\rm orb}$ & $f_{\rm RUWE}$ & $f_{\rm grazing}$ & $Q_{\rm gyro}$ &  Spec? \\
  -- &   -- & K & days & m\AA & Myr & Myr &    Earths &    days &      bool &   bool  & int & bool \\
	\hline
	\input{table_subgyr_confirmed} %\\
	%\hline
	\input{table_subgyr_candidate}
	\enddata
	\tablecomments{This table includes X, Y, Z... The machine-readable version,
		available online, includes additional columns for .... 
	}
\end{deluxetable*}
%\endlongtable

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{gyromodeldispersion.pdf}
		}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{li_vs_teff_koi_X_S19S21dquality_eagles_showpoints_nodata.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf The models.}
    Points represent $10^4$ draws from model probability distributions
    that have been fitted to observed rotation periods
    \citep{Bouma_2023} and lithium equivalent widths
    \citep[EWs;][]{Jeffries_2023} of stars in open clusters.  Lines
    are the ``mean models'' at various ages; the asymmetric intrinsic
    dispersion in rotation and lithium about these mean models, which
    is what the models fit, sets the theoretical precision limit for
    both age-dating methods.		Additional sources of uncertainty,
    including measurement uncertainty, impose further limits on
    achievable age precision.  These models are calibrated using open
    clusters younger than 4\,Gyr.  The displayed points assume a
    uniform distribution in temperature for visual clarity.
    The sizes of the points are the same in each panel, so that low
    apparent density signifies greater dispersion around the mean.
		\label{fig:models}
	}
\end{figure*}

@@

(Mention Linear prior in age.)

@@

\startlongtable
\begin{deluxetable*}{lllllllrrrrrr}
	%\tabletypesize{\footnotesize}
	\tabletypesize{\scriptsize}
	\tablecaption{Ages of Kepler planets and planet candidates.  Rows are sorted by the minimum of either the rotation or lithium-based age; this version of the table is truncated to planets younger than one billion years.  ``Confirmed'' planets appear before``candidate'' planets.
		The full machine-readable table contains ages and age limits for \nnonfopkoissomeageinfo\ non-false positive KOIs with MES$>$10.
		The bit quality flags for the rotation-based ages, $Q_{\rm gyro}$, are described in Section~\ref{subsec:flags}.
		%The non-truncated machine readable versions are accessible both
		%through the online journal, and at
		%\url{https://zenodo.org/record/8327508}.
		\label{tab:youngplanets}}
	%\toprule
	%\midrule
	%\endhead
	\startdata
  KOI & Kepler &  $T_{\rm eff}$ & $P_{\rm rot}$ & EW$_{\rm Li}$ & $t_{\rm gyro}$ & $t_{\rm Li} $ & $R_{\rm p}$ & $P_{\rm orb}$ & $f_{\rm RUWE}$ & $f_{\rm grazing}$ & $Q_{\rm gyro}$ &  Spec? \\
  -- &   -- & K & days & m\AA & Myr & Myr &    Earths &    days &      bool &   bool  & int & bool \\
	\hline
	\input{table_subgyr_confirmed} %\\
	%\hline
	\input{table_subgyr_candidate}
	\enddata
%	\tablecomments{This table includes X, Y, Z... The machine-readable version,
%		available online, includes additional columns for .... 
%	}
\end{deluxetable*}
%\endlongtable
